Dynamical modeling of tidal streams

### 2014-01-04 tex/ms.tex
streams: tweak about L_Z

The action and frequency distributions shown in
\figurename~\ref{fig:gd1_jt} combined with the knowledge that for
\emph{any} tidal stream the Hessian $(\partial^2 H / \partial \vecj
\partial \vecj)\large|_{\vecj^p}$ must be strongly dominated by a
single large eigenvalue leads me to propose that frequency--angle
space is a better coordinate system than action--angle space for
modeling tidal streams. That is, the distribution of actions in a
tidal stream has a complicated structure that is hard to capture using
a simple, analytic form (see also the discussion in
\citealt{Eyre11a}). Especially the ``bow tie'' structure in $(J_R,L_Z)$
and the overlapping leading- and trailing-arm distributions in
($J_R,J_Z$) are difficult to model with a simple distribution
function. The distribution of frequencies, however, is close-to one
dimensional, its direction of largest variance can be well-modeled as
a Gaussian (although below we will model it slightly differently), and
its parameters can all be easily estimated from the velocity
dispersion of the progenitor, the orbit of the progenitor, and the
gravitational potential, as discussed below. Therefore, we will model
tidal streams in frequency--angle space. Because the leading and
trailing arm are well-separated in frequency space, we model each arm
individually.

>>>>

The action and frequency distributions shown in
\figurename~\ref{fig:gd1_jt} combined with the knowledge that for
\emph{any} tidal stream the Hessian $(\partial^2 H / \partial \vecj
\partial \vecj)\large|_{\vecj^p}$ must be strongly dominated by a
single large eigenvalue leads me to propose that frequency--angle
space is a better coordinate system than action--angle space for
modeling tidal streams. That is, the distribution of actions in a
tidal stream has a complicated structure that is hard to capture using
a simple, analytic form (see also the discussion in
\citealt{Eyre11a}). Especially the ``bow tie'' structure in
$(J_R,L_Z)$ and the overlapping leading- and trailing-arm
distributions in ($J_R,J_Z$) are difficult to model with a simple
distribution function\footnote{For triaxial potentials, the azimuthal
  action $J_\phi \neq L_Z$ is the correct action to use instead of
  $L_Z$. Even though the modeling in this paper also applies to
  triaxial potentials, we denote $J_\phi$ as $L_Z$, because the
  simulation uses an axisymmetric potential.}. The distribution of
frequencies, however, is close-to one dimensional, its direction of
largest variance can be well-modeled as a Gaussian (although below we
will model it slightly differently), and its parameters can all be
easily estimated from the velocity dispersion of the progenitor, the
orbit of the progenitor, and the gravitational potential, as discussed
below. Therefore, we will model tidal streams in frequency--angle
space. Because the leading and trailing arm are well-separated in
frequency space, we model each arm individually.
